--- 
title: "Example Rmd for using the AMPL engine"
author: "Ruaridh Williamson"
---

First, set environment variables for each of the engine parameters.

Due to OptiRisk's annoying license manager, the system command
has to be invoked from the directory which contains the AMPL license.

Current workaround is to temporarily change the `knitr` working directory
to run the code before switching back to the default.

- `AMPL_EXE_DIR`: The directory which contains the `LICENSE.KEY` file
- `AMPL_EXE`: The AMPL executable relative to `AMPL_EXE_DIR`
- `SOLVER_EXE`: The solver executable relative to `AMPL_EXE_DIR`

```{r set_ampl_env, include=FALSE}
Sys.setenv(AMPL_EXE_DIR = "/Applications/AMPLDev.app/Contents/Resources",
           AMPL_EXE = "AMPL/ampl",
           SOLVER_EXE = "AMPL/cplex")
```

```{r}
# Define `ampl` engine based on knitr's already-defined `go` engine
knitr::knit_engines$set(ampl = function (options) {
  f = tempfile("code", ".", fileext = ".run")
  writeLines(code <- options$code, f)
  
  # Use absolute path so that the file can be found
  # after directory change
  f = normalizePath(f)
  on.exit(unlink(f), add = TRUE)
  
  # Change working directory and move back after code
  # chunk is complete
  cur_dir <- getwd()
  setwd(Sys.getenv("AMPL_EXE_DIR"))
  on.exit(setwd(cur_dir), add = TRUE)
  
  cmd = Sys.getenv("AMPL_EXE")
  fmt_args = sprintf("'%s'", f)
  tryCatch(system2(cmd, fmt_args, stdout = TRUE, stderr = TRUE, 
      env = options$engine.env), error = function(e) {
      if (!options$error) 
          stop(e)
  })
  run_args = sprintf("'%s'", f)
  extra = if (options$eval) {
      message("running: ", cmd, run_args)
      tryCatch(system2(cmd, run_args, stdout = TRUE, stderr = TRUE, 
          env = options$engine.env), error = function(e) {
          if (!options$error) 
              stop(e)
          "Error in executing ampl code"
      })
  }
  if (options$results == "hide") 
      extra = NULL
  knitr:::engine_output(options, code, extra)
})
```

```{ampl}
model '/Users/username/path_to_model/model.mod';
data '/Users/username/path_to_model/data.dat';

option solver '$SOLVER_EXE';
solve;
```
